### 2022-04-05 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@95f860b21612964841ed3849c3f84a0c23d5992b 🚀

\begin{itemize}
\tightlist
\item
  what are neutral landsacpes
\end{itemize}

@@

Originally based around methods for simulating spatially autocorrelated
data (Gardner \emph{et al.} 1987; Milne 1992).

whawt is spaital autocorrelation

they have seen use in a wide range of fields in ecology and evolution:
from landscape genetics (Storfer \emph{et al.} 2007), to landscape and
spatial ecology (Tinker \emph{et al.} 2004; Remmel \& Fortin 2013), and
biogeography (Albert \emph{et al.} 2017).

The two most popular libraries used to simulate neutral landscapes are
\texttt{NLMR} in (the \texttt{R} language) (Sciaini \emph{et al.} 2018)
and \texttt{NLMpy} (in Python; Etherington \emph{et al.} 2015). Here we
present \texttt{NeutralLandscapes.jl}, a package for neutral landscape
simulation in the \texttt{Julia} language. So, why another package? Here
we demonstrate that \texttt{NeutralLandscapes.jl} is orders of magnitude
faster than previous neutral landscape packages. In addition,
\texttt{NeutralLandscapes.jl} implements several novel methods for
simulating environmental change with temporal variation.

As biodiversity science becomes increasingly concerned with temporal
change and its consequences, its clear there is a gap in methodology in
generating neutral landscapes that change over time. Our model allows
users to simulate time-series of any \texttt{NeutralLandscape} layer,
and which produce an arbitrary distribution of change across every
spatial cell, with provided levels of spatial and temporal
autocorrelation.

>>>>

\begin{itemize}
\tightlist
\item
  what are neutral landscapes
\end{itemize}

@@

Different properties of landscapes (elevation, land cover, temperature)
vary across space in non-random ways. Tobler's law of geography:
``everything is related to everything else, but near things are more
related than distant things''

Originally based around methods for simulating spatially auto-correlated
data (Gardner \emph{et al.} 1987; Milne 1992).

they have seen use in a wide range of fields in ecology and evolution:
from landscape genetics (Storfer \emph{et al.} 2007), to spatial ecology
(Tinker \emph{et al.} 2004; Remmel \& Fortin 2013), and biogeography
(Albert \emph{et al.} 2017).

The two most popular libraries used to generate neutral landscapes are
\texttt{NLMR} in (the \texttt{R} language) (Sciaini \emph{et al.} 2018)
and \texttt{NLMpy} (in Python; Etherington \emph{et al.} 2015). Here we
present \texttt{NeutralLandscapes.jl}, a new package for neutral
landscape simulation in the \texttt{Julia} language. So, why create
another package?

Here we demonstrate that \texttt{NeutralLandscapes.jl} is orders of
magnitude faster than previous neutral landscape packages.

In addition, \texttt{NeutralLandscapes.jl} implements several novel
methods for simulating environmental change with temporal variation. As
biodiversity science becomes increasingly concerned with temporal change
and its consequences, its clear there is a gap in methodology in
generating neutral landscapes that change over time. Our model allows
users to simulate time-series of any \texttt{NeutralLandscape} layer,
and which can produce an arbitrary distribution of change across every
spatial cell, with provided levels of spatial and temporal
autocorrelation.
